The Skew-Normal Approximation of the Binomial Distribution

### 2010-12-24 pieces/final-paper/intro.tex
Added punctuation, support sets, made several small tweaks as suggested by Dr. Guffey.

\begin{equation*}
  f_X(x) = \binom{n}{x} p^x q^{n-x}
\end{equation*}

Calculating the binomial cdf, $F_X(x) = P(X \leq x) = \sum_{k=1}^x f_X(k)$, by
hand is manageable for small $n$ but quickly becomes cumbersome as $n$ grows
even mediumly large. A common strategy is to use the normal distribution as an
approximation:

\begin{equation}
  F_X(x) \approx \Phi \left( \frac{k + 0.5 - \mu}{\sigma} \right)
\end{equation}

@@

This approximation works well when either $n$ is very large (invoking the
Central Limit Theorem) or when $p$ is close to 0.5 (making $X$ roughly
symmetric). These rules of thumb are captured in a requirement, often stated as

\begin{equation*}
  np(1-p) > 9
\end{equation*}

or

\begin{align*}
      np &> 5 \quad \textnormal{for} \quad  0 < p \leq 0.5, \\
  n(1-p) &> 5 \quad \textnormal{for} \quad  0.5 < p < 1
\end{align*}

However, when $n$ is not large and $p$ is close to 0 or 1, the binomial
distribution is skewed and even if the above requrements are met, the
approximation can be inaccurate; sometimes, as demonstrated by \citet{mabs},
rather substantially. In these cases, the skew-normal approximation can provide
an alternative -- and considerably more accurate -- method of approximation.

>>>>

\begin{equation*}
  f_X(x) = \binom{n}{x} p^x q^{n-x}, \quad x = 0, 1, \ldots, n.
\end{equation*}

Calculating the binomial cdf, $F_X(x) = P(X \leq x) = \sum_{k=1}^x f_X(k)$, by
hand is manageable for small $n$ but quickly becomes cumbersome as $n$ grows
even moderately large. A common strategy is to use the normal distribution as
an approximation:

\begin{equation}
  F_X(x) \approx \Phi \left( \frac{x + 0.5 - \mu}{\sigma} \right),
\end{equation}

@@

This approximation works best when the binomial is perfectly symmetrical, with
$p=0.5$. However as $p$ travels away from 0.5 in either direction, the binomial
becomes increasingly skewed, and one must either compensate by providing ever
larger values of $n$ or face growing inaccuracy. In these cases, the
skew-normal approximation can provide a better alternative.
